Postural developments mediate children's visual access to social information

### 2018-01-30 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
incorporating of mike's remaining comments & a few trimming tries

From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like] and attend to the social information in their environment. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts  [@gredeback2008microstructure; @gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children -- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], and computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. Recent work also suggests dramatic changes in the child’s perspective over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

@@

Our final sample consisted of 36 infants and children, with 12 participants in three age groups: 8 months (6 females), 12 months (7 females), and 16 months (6 females). Participants were recruited from the surrounding community via state birth records, had no documented disabilities, and were reported to hear at least 80\% English at home. Demographics and exclusion rates are given in Table \ref{tab:pop}.  
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 Group & N & \% incl. & Avg age & Avg video length (min) \\ 
  \hline
   8 mo. &   12 & 0.46 & 8.71 & 14.41 \\ 
   12 mo. &  12 & 0.40 & 12.62 & 13.48 \\ 
   16 mo. &  12 & 0.31 & 16.29 & 15.00\\ 
   \hline
\end{tabular}
\caption{\label{tab:pop} Demographics by age group.}
\end{table}
To obtain this final sample, we tested `r length(all_subs$reason)` children, excluding  `r sum(all_subs$reason!="included")` children for the following reasons:
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam,
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing Communicative Development Inventory (CDI) data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and one excluded for sample symmetry. All inclusion decisions were made independent of the results of subsequent analyses. Some of these data were also used in @frank2013.

## Head-mounted camera
```{r headcam, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.label="headcam", fig.cap = "Field of view for two different headcam configurations (we used the lower in our current study)."}
img <- png::readPNG("images/viewangle_cut.png")
grid::grid.raster(img)
```

We used a small, head-mounted camera ("headcam") that was constructed from a MD80 model camera attached to a soft elastic headband. Videos captured by the headcam were 720x480 pixels with 25 frames per second. Detailed instructions for creating this headcam can be found  at \url{http://babieslearninglanguage.blogspot.com/2013/10/how-to-make-babycam.html}. A fisheye lens was attached to the camera to increase the view angle from $32^{\circ}$ horizontal by $24^{\circ}$ vertical to $64^{\circ}$ horizontal by $46^{\circ}$ vertical (see Figure \ref{fig:headcam}, left).

Even with the fish-eye lens, the vertical field of view of the camera is still considerably reduced compared to the child's approximate vertical field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces.

## Procedure
First, all parents signed consent documents while children were fitted with the headcam. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam [@yoshida2008]. After the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

@@

### Posture and Orientation Annotation
We created custom annotations to describe the child's physical posture (e.g. standing) and the orientation of the child relative to the caregiver (e.g. far away). The child's posture was categorized as being held/carried, prone (crawling or lying), sitting, or standing. The caregiver's orientation was characterized as being close, far, and behind the child (independent of distance). For the first two annotations (close/far from the child), the caregiver could either be to the front or side of the child. All annotations were made by a trained coder using the OpenSHAPA/Datavyu software. [@adolph2012], and times when the child was out of view of the tripod camera were marked as uncodable and were excluded from these annotations.

## Face and Hand Detection
We used three face detection systems to measure infants' access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones. We used this as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next tested the performance of two face detectors that both made use of recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract information about the position of 18 different body parts. For the second algorithm (called OpenPose) [@cao2017realtime], we used the agent's nose (one of the body parts detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

The OpenPose detector also provided us with the location of an agent's wrists, which we used as a proxy for hands for two reasons. First, as we did not capture childrens entire visual field. the presence of a wrist is likely often indicative of the presence of a hand within the field of view. Second, hands are often occluded by objects when caregivers are interacting with children, yet still visually accessible by the child and part of their joint interaction. 
### Algorithms
The first face detection system made use of a series of Haar feature-based cascade classifiers [@viola2004robust] applied to each individual frame.  The second algorithm (based on work by @zhang2016) uses multi-task cascaded convolutional neural networks (MTCNNs)  for joint face detection and alignment, built to perform well in real-world environments where varying illuminations and occlusions are present. We used a Tensorflow implementation of this algorithm avaliable at https://github.com/davidsandberg/facenet.

The CNN-based pose detector (OpenPose [@cao2017realtime; @simon2017hand; @wei2016cpm]) provided the locations of 18 body parts (ears, nose, wrists, etc.) and is available at https://github.com/CMU-Perceptual-Computing-Lab/openpose. The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of the body parts relevant to the face and hands (nose and wrists). We operationalized face detections as any frames containing a nose, and hand detections as any frames containing either the left or right wrist.

### Detector evaluation
To evaluate face detector performance, we hand-labeled  an unbiased "gold set" of labeled frames. To account for the relatively rare appearance of faces in the dataset, we thus h abeled two types of samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each child's video. For wrist detections, the "gold set" was constructed in the same manner, except frames with a high density of wrists came only from detections made by OpenPose.  Faces were classified as present if at least half of the face was showing; wrists were classified as present if any part of the wrist was showing.  Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2.

@@

For face detection, MTCNN outperformed OpenPose when taking into account only the composite F-score (`r round(perfFacesOverall$f[1],2)` MTCNN vs. `r round(perfFacesOverall$f[2],2)` OpenPose). Although MTCNN and OpenPose performed comparably with the random sample, MTCNN performed better on the high density sample (specifically looking at precision), suggesting that OpenPose generated more false positives than MTCNN. ViolaJones performed quite poorly relative to the other detectors, especially with respect to the random sample. We thus use MTCNN detections in the following analyses.

For wrist detection, OpenPose performed moderately well (F = `r round(perfWristsOverall$f,2)`) with relatively high precision but low recall on the randomly sampled frames (see Table 2). We thus analyze wrist detections, with the caveat that we are likely underestimating the proportion of wrists in the dataset.

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
   Algorithm & Sample\ Type & P & R & F \\ 
  \hline
  MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
  MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
  OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
  OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
  ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
  ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
  OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
  OpenPose-Wrists & Random & 0.88 & 0.29 & 0.43 \\ 
   \hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of faces detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\end{table}

@@

ggarrange(p1,p2)
```
We noted characteristic changes in infants' posture and orientation across this developmental time range. The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8 month-olds and 12 month-olds spent equivalent amounts of time either lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time either sitting or standing (see Figure \ref{fig:posture}).  We also observed characteristic changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

@@

We first examined the proportion of face and wrist detections across age; a summary can be seen in Figure \ref{fig:detByAge}. We observed a slight U-shaped function both when analyzing the output of the MTCNN and OpenPose detectors, such that 12-month-olds appeared to experience slightly fewer faces faces than 8 or 16-month-olds.

However, we found that any age related effects were much smaller compared to the impact of postural and locomotive changes on children's visual access to faces and wrists/hands. Children's posture was a major factor both in how many faces and wrists/hands they saw during the play session.  Infants who were sitting saw more faces than infants who were lying down or being carried, while infants who were standing saw the most faces (Figure \ref{fig:detByPosOrient}, upper panel); this same pattern was also true for wrists/hand detection. Children’s orientation also impacted their visual access to faces and hands. Children who were far away from their caregiver were more likely to see faces/hands than children who were close to their caregiver (Figure \ref{fig:detByPosOrient}, lower panel).

@@

To formalize these observations, we fit a generalized linear model to the proportion of faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p = `r round(faceGLMOut$coef[2,4],2)`). We also found the same pattern with respect to infants' visual access to hands (see Table 4); including interaction terms also eliminated any main effect of age on the proportion of wrists detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)`, p = `r round(wristGLMOut$coef[2,4],2)`). These results suggest that infants' visual access to social information is heavily influenced by their postural and locomotive developments.

@@

Finally, we explored how face and wrist/hand detections changed during object labeling events as a function of infant's posture and orientation. Specifically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. As before, we found that infants' posture and orientations impacted the degree to which they saw their caregiver's face and wrists during a labeling event; infants who were sitting or standing were more likely to have visual access to this social information. A full summary of the results can be seen in Figure \ref{fig:detByNaming}. However, we did not find that infants saw more faces or wrists/hands during naming events relative to baseline (average difference in proportion of wrists detected, 8 m.o. = `r round(wrists_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(wrists_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(wrists_naming$avgBaselineDiff[3],3)`;  average difference in proportion of faces detected, 8 m.o. = `r round(faces_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(faces_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(faces_naming$avgBaselineDiff[3],3)`).

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotive development impacts their visual access to social information, here operationalized as the presence of the faces and wrists of their caregiver. Children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically influenced the proportion of faces and wrists/hands that were available in the child's visual field. Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

This work also deploys novel advancements in computer vision to the study of developmental psychology. The field of object detection and recognition has advanced dramatically in the past five years, creating a new generation of algorithmic tools. These tools are substantially better equipped to deal with noisier, more complicated datasets and can extract richer and more detailed information.  As the headcams we used were inexpensive and the computer vision algorithms freely available, this method is a promising avenue for quantifying the visual and social information available to infant learners.

We suggest that the combined use of these new tools can be leveraged to understand the changing infant perspective on the visual world and the implications of these changes for linguistic, cognitive, and social development.

@@

Thanks to Kaia Simmons, Kathy Woo, Aditi Maliwal, and other members of the Language and Cognition Lab for help in recruitment, data collection, and annotation. This research was supported by a John Merck Scholars grant to MCF. An earlier version of this work was presented to the Cognitive Science Society in @frank2013. Please address correspondence to Michael C. Frank, Department of Psychology, Stanford University, 450 Serra Mall (Jordan Hall), Stanford, CA, 94305, tel: (650) 724-4003, email: \texttt{mcfrank@stanford.edu}.

# References

>>>>

From early infancy, children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like]. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts  [@gredeback2008microstructure; @gredeback2010development]. Further, when infants attend to video stimuli, they tend to look mostly at faces at the expense of other visual information -- though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

@@

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children -- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], and computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. This perspective changes over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

@@

Our final sample consisted of 36 infants and children, with 12 participants in three age groups: 8 months (6 females), 12 months (7 females), and 16 months (6 females). Participants were recruited from the surrounding community via state birth records, had no documented disabilities, and were reported to hear at least 80\% English at home. Demographics and exclusion rates are given in Table \ref{tab:pop}.  
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 Group & N & \% incl. & Avg age & Avg video length (min) \\ 
  \hline
   8 mo. &   12 & 0.46 & 8.71 & 14.41 \\ 
   12 mo. &  12 & 0.40 & 12.62 & 13.48 \\ 
   16 mo. &  12 & 0.31 & 16.29 & 15.00\\ 
   \hline
\end{tabular}
\caption{\label{tab:pop} Demographics by age group.}
\end{table}
To obtain this final sample, we tested `r length(all_subs$reason)` children, excluding  `r sum(all_subs$reason!="included")` children for the following reasons:
`r sum(all_subs$reason=="HC technical error")` for technical issues related to the headcam,
`r sum(all_subs$reason=="would not wear camera")` for failing to wear the headcam,
`r sum(all_subs$reason=="less than 4 min HC footage")` for fewer than 4 minutes of headcam footage,
`r sum(all_subs$reason=="multiple people")` for having multiple adults present,
`r sum(all_subs$reason=="no CDI")` for missing Communicative Development Inventory (CDI) data,
`r sum(all_subs$reason=="no DV cam footage")` for missing scene camera footage,
`r sum(all_subs$reason=="infant crying")` for fussiness, and one for sample symmetry. All inclusion decisions were made independent of the results of subsequent analyses. Some of these data were also analyzed in @frank2013.

## Head-mounted camera
```{r headcam, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=3, set.cap.width=T, num.cols.cap=1, fig.label="headcam", fig.cap = "Vertical field of view for two different headcam configurations (we used the lower in our current study)."}
img <- png::readPNG("images/viewangle_cut.png")
grid::grid.raster(img)
```

We used a small, head-mounted camera ("headcam") that was constructed from a MD80 model camera attached to a soft elastic headband. Videos captured by the headcam were 720x480 pixels with 25 frames per second. Detailed instructions for creating this headcam can be found  at \url{http://babieslearninglanguage.blogspot.com/2013/10/how-to-make-babycam.html}. A fisheye lens was attached to the camera to increase the view angle from $32^{\circ}$ horizontal by $24^{\circ}$ vertical to $64^{\circ}$ horizontal by $46^{\circ}$ vertical (see Figure \ref{fig:headcam}, bottom).

Even with the fish-eye lens, the vertical field of view of the camera is still considerably reduced compared to the child's approximate vertical field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces, understanding that this decision limited our ability to detect hands (especially those of the child, which are typically found at the bottom of the visual field)

## Procedure
All parents signed consent documents while children were fitted with the headcam. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam [@yoshida2008]. When the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

@@

### Posture and Orientation Annotation
We created custom annotations to describe the child's physical posture (e.g. standing) and the orientation of the child relative to the caregiver (e.g. far away). The child's posture was categorized as being held/carried, prone (crawling or lying), sitting, or standing. The caregiver's orientation was characterized as being close, far, or behind the child (independent of distance). For the first two annotations (close/far from the child), the caregiver could either be to the front or side of the child. All annotations were made by a trained coder using the OpenSHAPA/Datavyu software [@adolph2012]. Times when the child was out of view of the tripod camera were marked as uncodable and were excluded from these annotations.

## Face and Hand Detection
We used three face detection systems to measure infants' access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones. We used this algorithm as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next tested the performance of two face detectors that both made use of recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract information about the position of 18 different body parts. For the second algorithm [OpenPose, @cao2017realtime], we used the agent's nose (one of the body parts detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

The OpenPose detector also provided us with the location of an agent's wrists, which we used as a proxy for hands for two reasons. First, as we did not capture childrens entire visual field. the presence of a wrist is likely often indicative of the presence of a hand within the field of view. Second, hands are often occluded by objects when caregivers are interacting with children, yet still visually accessible by the child and part of their joint interaction. For example, if a caregiver was holding a toy andpresenting it to the infant, their wrists may be visible but theirhand may not necessarily be (as it is occluded by the toy).

### Algorithms
The first face detection system made use of a series of Haar feature-based cascade classifiers [@viola2004robust] applied to each individual frame.  The second algorithm (based on work by @zhang2016) uses multi-task cascaded convolutional neural networks (MTCNNs)  for joint face detection and alignment, built to perform well in real-world environments where varying illuminations and occlusions are present. We used a Tensorflow implementation of this algorithm avaliable at https://github.com/davidsandberg/facenet.

The CNN-based pose detector  [OpenPose, @cao2017realtime; @simon2017hand; @wei2016cpm]) provided the locations of 18 body parts (ears, nose, wrists, etc.) and is available at https://github.com/CMU-Perceptual-Computing-Lab/openpose. The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of the body parts relevant to the face and hands (nose and wrists). We operationalized face detections as any frames containing a nose, and hand detections as any frames containing either the left or right wrist.

### Detector evaluation
To evaluate face detector performance, we hand-labeled  an "gold set" of labeled frames. To account for the relatively rare appearance of faces in the dataset, we  hand abeled two types of samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each child's video. For wrist detections, the "gold set" was constructed in the same manner, except frames with a high density of wrists came only from detections made by OpenPose.  Faces were classified as present if at least half of the face was showing; wrists were classified as present if any part of the wrist was showing.  Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2.

@@

For face detection, MTCNN outperformed OpenPose when taking into account only the composite F-score (`r round(perfFacesOverall$f[1],2)` MTCNN vs. `r round(perfFacesOverall$f[2],2)` OpenPose). Although MTCNN and OpenPose performed comparably with the random sample, MTCNN performed better on the high density sample (specifically looking at precision), suggesting that OpenPose generated more false positives than MTCNN. ViolaJones performed quite poorly relative to the other detectors, especially with respect to the random sample. We thus use MTCNN detections in the following analyses. For wrist detection, OpenPose performed moderately well (F = `r round(perfWristsOverall$f,2)`) with relatively high precision but low recall on the randomly sampled frames (see Table 2). We thus analyze wrist detections, with the caveat that we are likely underestimating the proportion of hands in the dataset.

\begin{table}[ht]
\centering
\begin{tabular}{rllrrr}
  \hline
   Algorithm & Sample\ Type & P & R & F \\ 
  \hline
  MTCNN-Faces & High density & 0.89 & 0.92 & \textbf{0.90} \\ 
  MTCNN-Faces & Random & 0.94 & 0.62 & 0.75 \\ 
  OpenPose-Faces & High density & 0.78 & 0.93 & 0.84 \\ 
  OpenPose-Faces & Random & 0.72 & 0.80 & \textbf{0.76} \\ 
  ViolaJones-Faces & High density & 0.96 & 0.44 & 0.60 \\ 
  ViolaJones-Faces & Random & 0.44 & 0.38 & 0.41 \\ 
  OpenPose-Wrists & High density & 0.66 & 1.00 & 0.79 \\ 
  OpenPose-Wrists & Random & 0.88 & 0.29 & 0.43 \\ 
   \hline
\end{tabular}
\caption{Detector performance on both high density samples (where proportion of targets detected was high) and random samples (where frames were randomly selected). P, R, and F denote precision, recall, and F-score, respectively. Scores in bold are the highest F-scores for each sample type.} 
\end{table}

@@

ggarrange(p1,p2)
```
The proportion of time infants spent sitting decreased with age, and the proportion of time infants spent standing increased with age. Both 8 month-olds and 12 month-olds spent equivalent amounts of time lying/crawling, which was markedly decreased in the 16-month-olds, who spent most of their time sitting or standing (see Figure \ref{fig:posture}).  We also observed changes in children's orientation relative to their caregivers: the 8-month-olds spent more time with their caregiver behind them supporting their sitting positions (see Figure \ref{fig:posture}).

@@

We examined the proportion of face and wrist detections across age (see Figure \ref{fig:detByAge}). We observed a slight U-shaped function in face detections, such that 12-month-olds appeared to have visual acces to slightly fewer faces faces than 8 or 16-month-olds; conversely, wrist detections perhaps appeared to generally increase with age.

Age related effects were much smaller than postural and locomotive changes on children's visual access to faces and wrists/hands. Children's posture was a major factor both in how many faces and wrists/hands they saw during the play session. Infants who were sitting saw more faces than infants who were lying down or being carried, while infants who were standing saw the most faces (Figure \ref{fig:detByPosOrient}, upper panel); this same pattern was also true for wrists/hand detections. Children’s orientation also impacted their visual access to faces and hands: children who were far away from their caregiver were more likely to see faces/hands than children who were close to their caregiver (Figure \ref{fig:detByPosOrient}, lower panel).

@@

To formalize these observations, we fit a generalized linear model to the proportion of faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p = `r round(faceGLMOut$coef[2,4],2)`). We also found the same pattern with respect to infants' visual access to hands (see Table 3); including interaction terms also eliminated any main effect of age on the proportion of wrists detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)`, p = `r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants' visual access to social information is mediated by their posture and orientation, which is in turn a function of their general locomotor development (as indexed by chronological age).

@@

Finally, we explored how face and wrist detections changed during object labeling events as a function of infant's posture and orientation. We analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and synchronized with the frame-by-frame face/wrist detections. We found that infants' posture and orientations mediated their visual access to faces and wrists/hands during labeling events; infants who were sitting or standing were more likely to have visual access to this social information (see Figure \ref{fig:detByNaming}). However, we did not find that infants saw particularily more faces or wrists/hands during naming events relative to baseline (avg. difference in proportion of wrists, 8 m.o. = `r round(wrists_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(wrists_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(wrists_naming$avgBaselineDiff[3],3)`;  avg. difference in proportion of faces, 8 m.o. = `r round(faces_naming$avgBaselineDiff[1],3)`, 12 m.o. = `r round(faces_naming$avgBaselineDiff[2],3)`, 16 m.o. = `r round(faces_naming$avgBaselineDiff[3],3)`).

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotive development impacts their visual access to social information, here operationalized as the presence of the faces and wrists of their caregiver. Children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically influenced the proportion of faces and wrists/hands that were available in the child's visual field. Broadly, this work suggests that motor development mediates how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.  More work is needed to understand how these results relate to the pattern of activities and social interctions observed in children's home experiences [@fausey2016].

This work also deploys novel advancements in computer vision to the study of developmental psychology. The field of object detection and recognition has advanced dramatically in the past five years, creating a new generation of algorithmic tools. These tools are substantially better equipped to deal with noisier, more complicated datasets and can extract richer and more detailed information than classic models of face detection (i.e., ViolaJones). As the headcams we used were inexpensive and the computer vision algorithms freely available,  suggest that the combined use of these new tools can be leveraged to understand the changing infant perspective on the visual world and the implications of these changes for linguistic, cognitive, and social development.

@@

Thanks to Kaia Simmons, Kathy Woo, and Aditi Maliwal for help in recruitment, data collection, and annotation. An earlier version of this work was presented to the Cognitive Science Society in @frank2013. 
# References
